Analysis of observational data, to calculate the Delayed-Tau model parameters

### 2025-02-04 thesis.qmd
common galaxy count

Before we merge the two catalogs we need to compare the corresponding quantities to ensure that there are no major incompatabilities. The quantities that are comparable are:

-   Distances \[Mpc\]
-   Radial Velocities \[km/s\]
-   Morphology and Geometry of the galaxies
    -   Morphological type (Numerical Hubble)
    -   Inclination \[degrees\]
    -   Angular Diameter of the Major and Semi-major axis \[arcmin\]
-   K-band Luminosity \[$L_\odot$\]
-   K and B-band Magnitudes \[mag\]
-   Star Formation Rates \[$M_\odot/yr$\]

>>>>

Before we merge the two catalogs we need to compare the corresponding quantities of the 288 common galaxies to ensure that there are no major incompatabilities. The quantities that are comparable are:

-   Distances \[Mpc\] (288/288 galaxies)
-   Radial Velocities \[km/s\] (286/288 galaxies)
-   Morphology and Geometry of the galaxies
    -   Morphological type (229/288 galaxies)
    -   Inclination \[degrees\] (209/288 galaxies)
    -   Angular Diameter of the Major and Semi-major axis \[arcmin\] (261/288 galaxies)
-   K-band Luminosity \[$L_\odot$\] and Magnitude (70/288 galaxies)
-   B-band Magnitudes \[mag\] (244/288 galaxies)
-   Star Formation Rates \[$M_\odot/yr$\] (73/288 galaxies)
